A secondary screen architecture to accurately capture viewers' interactions in an iTV environment

### 2014-05-14 src/paper.tex
Changes in title and abstract

\title{A secondary screen architecture to accurately capture viewers' interactions and contextual information in TV environments}

@@

\begin{abstract}
TV watching is frequently seen as a social activity. People gather around the television for entertainment or information. Advances in TV technology have enabled the viewer to actively interact with the TV through interactive applications instead of just passively watch TV. Since the TV set is shared by many people and the interaction occur by using a single remote control, it is difficult to accurately capture the individual interactions from every viewer. It is also difficult to identify the context in which the interactions occur, e.g., the people that are present in the environment. In this paper, we present an architecture that facilitates viewers' individual interactions and contextual information in shared TV environments. One important application for this data consists in generating personalized content for single viewers and groups of viewers.
\end{abstract}

>>>>

\title{A secondary screen architecture to accurately capture viewers' interactions in an iTV environment}

@@

\begin{abstract}
TV watching is frequently seen as a social activity. People gather around the television for entertainment or information. Advances in TV technology have enabled the viewer to actively interact with the TV through interactive applications instead of just passively watch TV. Since the TV set is shared by many people and the interaction occur by using a single remote control, it is difficult to accurately capture the individual needs from each viewer. It is also difficult to identify the context in which the interactions occur, e.g., to manage uniquely who is present in the environment and what is being watched on TV. In this paper, we present an architecture that facilitates viewers' individual interactions and contextual information in shared TV environments. One important application for this data consists in generating personalized content for single viewers and groups of viewers.
\end{abstract}
